Anxiety: a decision-theoretic perspective

### 2019-01-28 manuscript/manuscript.tex
overhaul of figures. need to finish few more

@@

@@

Discuss previous computational approaches: This has also been previously been
investigated in previous computational modeling \citep{Huys2009}. There
the authors found that beliefs about a lack of controllability, mechanistically
modeled as corrupted priors about action-outcome contingencies, found deficient
learning in novel environments. The present results are no doubt related, but
address a different environment and a different behavior.

>>>>

% I think you want to explain second order conditioning in PTSD in this context.

@@

Review the original findings of the papers. Aversive pruning as a means of
limiting computational demands in forward planning in complex sequential
environments. Remark that this is a sensible theory and we are not attempting to
argue against it.

Rather we are trying to show that our theory makes similar predictions in the
sorts of tasks. Combine that with expectations of one's own incompetency, and
maybe its not all that surprising. Combine this with working memory deficits
in anxiety, and maybe its doubly not surprising. So... Yeah.

There are ways to teasing this apart.

@@

Discuss previous computational approaches: This has also been previously been
investigated in previous computational modeling \citep{HuysDayan2009}. There
the authors found that beliefs about a lack of controllability, mechanistically
modeled as corrupted priors about action-outcome contingencies, found deficient
learning in novel environments. The present results are no doubt related, but
address a different environment and a different behavior.
